Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-09 WSSSPE3/report/wg_appendix_publishing_SW.tex
Replied to Dan's note.
Added text stating that the executable paper website going live in January and mentioned the need for ongoing curation.
small fixes

The only obstacle to this is the difficulty in finding and identifying such
publications. The Software Sustainability Institute was able to do something
similar for publications about software by making a public page \choinote{where?} containing a
catalog of these publications and enlisting the help of the community to grow
the list.

@@

Create the first version of the web page to be displayed on the Software
Sustainability Institute's website: \url{http://www.software.ac.uk}.
\katznote{when?}

@@

Steven R.\ Brandt will create a first version of the page within a week or so of
the WSSSPE3 conference.

Neil Chue Hong will take responsibility for the page once it is up.

>>>>

The only obstacle to this is the difficulty in finding and identifying such
publications. The Software Sustainability Institute was able to do something
similar for publications about software by making a public page on the Software
Sustainability Institute's website (\url{http://www.software.ac.uk}) containing a
catalog of these publications and enlisting the help of the community to grow
the list.

@@

Create the first version of the web page to be displayed on the Software
Sustainability Institute's website: \url{http://www.software.ac.uk}.
We expect the page to be live in early January of 2016.

An ongoing effort to update the page should follow.

@@

Steven R.\ Brandt has created a first version of the page, and it is in the process
of being posted on the Software
Sustainability Institute's website: \url{http://www.software.ac.uk}. 
Neil Chue Hong will take responsibility for the page once it is up.
